Efficient Community Formation \\ for Web Services

### 2013-12-30 papers/coalition-journal-R1/coalition_journal_r1.tex
changes

In this direction, recently \cite{DBLP:conf/IEEEscc/LimTMB12,
DBLP:conf/IEEEscc/KhosravifarABT11, 10.1109/TSC.2012.12} proposed
mechanisms to help users and services maximize their gain. A
two-player non-cooperative game between web services and community
master was introduced in
\cite{DBLP:conf/IEEEscc/KhosravifarABT11}. In this game-theoretic
model, the strategies available to a web service when facing a new
community are requesting to join the community, accepting the
master's invitation to join the community, or refusing the
invitation to join. The set of strategies for communities are
inviting the web service or refusing the web service's join
request. Based on their capacity, market share and reputation, the
two players have different sets of utilities over the strategy
profiles of the game. The main limits of this game model are: 1)
its consideration of only three quality parameters, while the
other factors are simply ignored; and 2) the non-consideration of
the web services already residing within the community. The game
is only between the community master and the new web service, and
the inputs from all the other members and their influence on the
master's decision are simply ignored. The consideration of those
inputs and this influence factor is a significant issue as
existing web services can lose utility or payoff because of the
new member, which can results in an unhealthy and unstable group.
The problem comes from the fact that the existing members should
collaborate with the new web services, so probably their
performance as a group can suffer. Existing members may even
deviate and try to join other communities if they are unsatisfied.
Those considerations of forming stable and efficient coalitions
are the main contributions of our paper.

@@

\textbf{Web Service Community.}
Community of web services is a collection of web services with same functionallity having a 
unique manager and communication end point, which is the access point to the community.

\cite{DBLP:journals/internet/BenatallahSD03,
Zeng:2003:QDW:775152.775211}, the authors introduce community of
web services as collection of cooperative web services with common
functionalitiers but different QoS metrics. Therefore
$communities$ are differentiated from $composition$ types of web
service cooperation in which web services with different
functionalities work together to generate a new service with
composite functionality.

In \cite{DBLP:journals/internet/BenatallahSD03}, Behatallah et al. defined communities as \emph{Service Containers} which aggregates substitutable web services providing a common functionality (same set of operations). They abstracted these \emph{Service Containers} as web services which are created, advertised, discovered and invoked just as elementary web services, they \emph{Container} as a manager is responsible for the mentioned tasks and also web service selection upon recieving a request on run-time. They have proposed a scoring service based on non-functional requrement of the task and web service capabilties to dynamicly chose the web service to perform the task upon reciving requests. A similar concept was proposed in \cite{DBLP:journals/ijebr/MaamarSTBB09}. They introduced web service coimmunities as a collection of web services with a common functionality but different QoS properties. A community manager upon recieving a request, delegates the request to one of its current members. The choice is based on history and quality metrics of each web service. They have proposed an efficient global web service selection algorithm in order to approach quality constraints and preferences for composite services which requres aggregation of different type of services to satisfy a request.

Benslimane et al. \cite{Liris-2770} have proposed multi-layer approach, grouping similar Web services into communities and having an interface implemented as an asbtract Web service for accessing the community on top of the community layer. The intractions between composite, management and community layers and the bindings are performed by a generic driver called Open Software Connectivity (OSC).

@@

%%%%%%%%%%%%%%%%% OLD
Maamar et al. initially in \cite{conf/webist/MaamarLBTS07} and
then comprehensively in \cite{DBLP:journals/ijebr/MaamarSTBB09}
proposed an architecture utilizing \emph{Contract-Net} protocol
for engineering task distribution within communities.

This architecture has been further developed in
\cite{conf/IEEEscc/BenharrefSBB11, conf/IEEEscc/KhosravifarBMMT10,
conf/aina/LimTM11, CSTintercommunity}. Two types of roles have
been distinguished for community members: masters and slaves.
Master web services lead communities and are responsible for
membership management. They can invite and convince slave web
services to join the community, and attract new slave web services
to their communities by awarding them better payoff. Moreover,
they can eject some slave members from the community to improve
its overall reputation if these members are misbehaving or cannot
provide the promised QoS \cite{DBLP:journals/ijebr/MaamarSTBB09}.
%%%%%%%%%%%%%%%%% OLD

@@

\emph{3) Users} generate requests and try to find the best
available services. User satisfaction is abstracted as function of
quantity and quality of tasks accomplished by a given service.
Higher user satisfaction leads to higher trust an better
reputation of the community as a whole, which helps direct more
requests towards that community.

@@

\emph{Shapley value} is a unique and fair solution concept for
payoff distribution among the members of the coalition. It
basically rewards members with the amount of average marginal
contribution they add to the coalition. It checks the contribution
of member $i$ by adding the agent to all possible subsets of
coalitions $S$, where $S \subseteq N-\{i\}$. If he is added to the
set $S$, his contribution to the coalition is $v(S \cup
\left\{i\right\}) - v(S)$. Average marginal contribution of agent
$i$'s is calculated by averaging this value over all possible
subsets of $N$, in the Shapley value equation (Equation
\ref{eq:shapley}).

@@

Our algorithm works as follows. Given an established community
with a coordinator and some member web services, a web service would
send a \emph{join request} to join  the community. Ideally, the
\emph{core} or \emph{$\epsilon$-core} stability of the group
having this new member should be analyzed. As the normal core
membership algorithm is computationally intractable, we exploit
Proposition \ref{proposition1} and Equation \ref{eq:convex_snow}
to check the convexity of our game having characteristic function
where the new member is added. In this equation (i.e., Equation
\ref{eq:convex_snow}), let $C$ be our community members before the
new web service joins the community. Let  ${i}$ be the new web
service, and then verify the equation for $S$, setting $ S = T /
W1 $ where $W1$ is the set of all possible subsets of the set $N$
having the size $1$. We can relax the equation a bit by adding a
constant $\epsilon$ to the left side of the equation. We call this
method \emph{Depth-1 Convex-Checker} algorithm. If the equation is
satisfied for all $W1$, we let the new web service joins our
community, since the web service will contribute positively enough
to make our new community stable. Since only subsets of size $1$
are checked, the following Proposition holds.

@@

We discussed $core$ as one of the prominent solution concepts in
cooperative games. Working together, completing tasks and
generating revenue, agents need to distribute the gain in a way no
agents would gain more by having their own group. However, in most
cases the core of a game is empty so we introduced the
\emph{$\epsilon$-core} concept, where agents would only earn a
minimal amount of $\epsilon$ by deviating. Stability is an
attractive property for communities. In addition, communities
would benefit by having slightly more web services than the exact
number of web services needed to satisfy the task rate cap. This
is because there is always a possibility that the web services may
leave the community or they may under perform and degrade the
quality values they were initially performing with.

@@

As mentioned in Section \ref{s:preliminaries}, the concept of
\emph{core}, assumes no coalition of players can gain anything by
deviating, which is a fairly strong requirement, and that is why
the notion of \emph{$\epsilon$-core} was introduced. Least-Core
$e(G)$ of a game $G$, is the minimum amount of $\epsilon$ so that
the core is not empty. We evaluated the non-emptiness of
\emph{$\epsilon$-core} set using the valuation function and a set
of web services. We picked random number of web services from the
dataset and formed around 10,000 random coalitions consisting of 3
to 26 web services. We choose 26 as the maximum number of members
in our coalition since it is computationally very complex for
larger coalitions to verify whether \emph{$\epsilon$-core} set is
empty or not. Also instead of considering $\epsilon$ amount of
constant deviation in \emph{$\epsilon$-core} definition (Equation
\ref{eq:core2}), we similarly defined \emph{relative
$\epsilon$-core} concept where no coalition would benefit more
than \emph{$\epsilon$ $\times$ v(C)} by deviating. We set
$\epsilon$ between 0 and 1 and verify the \emph{relative
$\epsilon$-core} set non-emptiness. The results in Figure
\ref{f_leastcore} illustrates that almost 10\% of our random web
service coalitions have non-empty \emph{core} solution and
\emph{$\epsilon$-core} solution is \emph{always} non-empty when we
let agents gain only 30\% more of $v(C)$ by deviating.

>>>>

In this direction, recently \cite{DBLP:conf/IEEEscc/LimTMB12,
DBLP:conf/IEEEscc/KhosravifarABT11, 10.1109/TSC.2012.12} proposed
mechanisms to help users and services maximize their gain. A
two-player non-cooperative game between web services and community
master was introduced in
\cite{DBLP:conf/IEEEscc/KhosravifarABT11}. In this game-theoretic
model, the strategies available to a web service when facing a new
community are requesting to join the community, accepting the
master's invitation to join the community, or refusing the
invitation to join. The set of strategies for communities are
inviting the web service or refusing the web service's join
request. Based on their capacity, market share and reputation, the
two players have different sets of utilities over the strategy
profiles of the game. The main limits of this game model are: 1)
its consideration of only three quality parameters, while the
other factors are simply ignored; and 2) the non-consideration of
the web services already residing within the community. The game
is only between the community master and the new web service, and
the inputs from all the other members and their influence on the
master's decision are simply ignored. The consideration of those
inputs and this influence factor is a significant issue as
existing web services can lose utility or payoff because of the
new member, which can result in an unhealthy and unstable group.
The problem comes from the fact that the existing members should
collaborate with the new web services, so probably their
performance as a group can suffer. Existing members may even
deviate and try to join other communities if they are unsatisfied.
Those considerations of forming stable and efficient coalitions
are the main contributions of our paper.

@@

\textbf{Web Service Community.}
Community of web services is a collection of web services with same functionallity having a 
coordinator and communication end point, which is the access point to the community. In \cite{DBLP:journals/internet/BenatallahSD03}, Behatallah et al. defined communities as \emph{Service Containers} which aggregates substitutable web services providing a common functionality (same set of operations). They abstracted \emph{Service Containers} as web services which are created, advertised, discovered and invoked just as elementary web services, they \emph{Container} as a manager is responsible for the mentioned tasks and also web service selection upon recieving a request on run-time. They have proposed a scoring service based on non-functional requrement of the task and web service capabilties to dynamicly chose the web service to perform the task upon reciving requests. A similar concept was proposed in \cite{DBLP:journals/ijebr/MaamarSTBB09}. They introduced web service coimmunities as a collection of web services with a common functionality but different QoS properties. A community manager upon recieving a request, delegates the request to one of its current members. The choice is based on history and quality metrics of each web service. They have proposed an efficient global web service selection algorithm in order to approach quality constraints and preferences for composite services which requres aggregation of different type of services to satisfy a request.

Benslimane et al. \cite{Liris-2770} have proposed a multi-layer approach, grouping similar Web services into communities and having an interface implemented as an asbtract Web service for accessing the community on top of the community layer. The intractions between composite, management and community layers and the bindings are performed by a generic driver called Open Software Connectivity (OSC).

@@

Maamar et al. initially in \cite{conf/webist/MaamarLBTS07} and
then comprehensively in \cite{DBLP:journals/ijebr/MaamarSTBB09}
proposed an architecture utilizing \emph{Contract-Net} protocol
for engineering task distribution within communities of web services.

This architecture has been further developed in
\cite{conf/IEEEscc/BenharrefSBB11, conf/IEEEscc/KhosravifarBMMT10,
conf/aina/LimTM11, CSTintercommunity}. Two types of roles have
been distinguished for community members: masters and slaves.
Master web services lead communities and are responsible for
membership management. They can invite and convince slave web
services to join the community, and attract new slave web services
to their communities by awarding them better payoff. Moreover,
they can eject some slave members from the community to improve
its overall reputation if these members are misbehaving or cannot
provide the promised QoS \cite{DBLP:journals/ijebr/MaamarSTBB09}.

In \cite{Medjahed05adynamic} authors developed a community as a ``container'' that clusters Web services based on a specefic area of interest. All web services in a given community, share the same functionality. These communities are created by \emph{third party community prividers} which use the \emph{community ontology} as a template and define a set of operations that all web services within a community should provide. Using semantic analysis on web service operations, web services either find and join a community with similar functionality or create a new operation description for a new community.

@@

\emph{3) Users} generate requests and try to find the best
available services. User satisfaction is abstracted as function of
quantity and quality of tasks accomplished by a given service.
Higher user satisfaction leads to higher trust and better
reputation of the community as a whole, which helps direct more
requests towards that community.

@@

\emph{Shapley value} is a unique and fair solution concept for
payoff distribution among the members of the coalition. It
basically rewards members with the amount of average marginal
contribution they add to the coalition. It checks the contribution
of member $i$ by adding the agent to all possible subsets of
coalitions $S$, where $S \subseteq N-\{i\}$. If member $i$ is added to the
set $S$, its contribution to the coalition is $v(S \cup
\left\{i\right\}) - v(S)$. Average marginal contribution of agent
$i$'s is calculated by averaging this value over all possible
subsets of $N$, in the Shapley value equation (Equation
\ref{eq:shapley}).

@@

Our algorithm works as follows. Given an established community
with a coordinator and some member web services, a web service would
send a \emph{join request} to join  the community. Ideally, the
\emph{core} or \emph{$\epsilon$-core} stability of the group
having this new member should be analyzed. As the normal core
membership algorithm is computationally intractable, we exploit
Proposition \ref{proposition1} and Equation \ref{eq:convex_snow}
to check the convexity of our game having characteristic function
where the new member is added. In this equation (i.e., Equation
\ref{eq:convex_snow}), let $C$ be our community members before the
new web service joins the community. Let  ${i}$ be the new web
service, and then verify the equation for $S$, setting $ S = T /
W1 $ where $W1$ is the set of all possible subsets of the set $N$
having the size $1$. We can relax the equation a bit by adding a
constant $\epsilon$ to the left side of the equation. We call this
method \emph{Depth-1 Convex-Checker} algorithm. If the equation is
satisfied for all $W1$, we let the new web service join our
community, since the web service will contribute positively enough
to make our new community stable. Since only subsets of size $1$
are checked, the following Proposition holds.

@@

We discussed $core$ as one of the prominent solution concepts in
cooperative games. Working together, completing tasks and
generating revenue, agents need to distribute the gain in a way no
agents would gain more by forming their own group. However, in most
cases the core of a game is empty so we introduced the
\emph{$\epsilon$-core} concept, where agents would only earn a
minimal amount of $\epsilon$ by deviating the coalition. Stability is an
attractive property for communities. In addition, communities
would benefit by having slightly more web services than the exact
number of web services needed to satisfy the task rate cap. This
is because there is always a possibility that the web services may
leave the community or they may under perform and degrade the
quality values they were initially performing with.

@@

As mentioned in Section \ref{s:preliminaries}, the concept of
\emph{core}, assumes no coalition of players can gain anything by
deviating, which is a fairly strong requirement, and that is why
the notion of \emph{$\epsilon$-core} was introduced. Least-Core
$e(G)$ of a game $G$, is the minimum amount of $\epsilon$ so that
the core is not empty. We evaluated the non-emptiness of
\emph{$\epsilon$-core} set using the valuation function and a set
of web services. We picked random number of web services from the
dataset and formed around 10,000 random coalitions consisting of 3
to 26 web services. We choose 26 as the maximum number of members
in our coalition since it is computationally very complex for
larger coalitions to verify whether \emph{$\epsilon$-core} set is
empty or not. Also instead of considering $\epsilon$ amount of
constant deviation in \emph{$\epsilon$-core} definition (Equation
\ref{eq:core2}), we similarly defined \emph{relative
$\epsilon$-core} concept where no coalition would benefit more
than \emph{$\epsilon$ $\times$ v(C)} by deviating. We set
$\epsilon$ between 0 and 1 and verify the \emph{relative
$\epsilon$-core} set non-emptiness. We add a random web service to a random already stable community of web services.
The results in Figure \ref{f_leastcore} illustrates that almost 10\% of new communities will stay stable and will have non-empty \emph{core} solution and
\emph{$\epsilon$-core} solution is \emph{always} non-empty when we
let agents gain only 30\% more of $v(C)$ by deviating.
